Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-11-27 main.tex
:pencil: Add backscatter sum-capacity and primary ergodic capacity

			Without loss of generality, we focus on the transmissions and detections during one particular backscatter symbol period. To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard CSCG distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-PSK modulation by \eqref{eq:mpsk}, i.e., $c_k \in \mathcal{C}$, $\forall k \in \mathcal{K}$. Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.}
			\begin{equation}
				y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k\right) \boldsymbol{w} s[n] + w[n],
				\label{eq:received_signal}
			\end{equation}
			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ is the equivalent Additive White Gaussian Noise (AWGN) at block $n$. Besides, we stack the backscatter symbol of $K$ tags as $\boldsymbol{c} \triangleq [c_1,\ldots,c_K]^T \in \mathcal{C}^{K \times 1}$, the received signal over $N$ blocks as $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
			\begin{equation}
				h_{\mathrm{E}}^H(\boldsymbol{c}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k.
				\label{eq:equivalent_channel}
			\end{equation}

@@

			\begin{remark}
				One key property of symbiotic radio is the primary message propagates to the user from a known channel and multiple multiplicative channels with uncertainty introduced by backscatter modulation. As such, each reflection coefficient simultaneously encodes the tag message and influences the equivalent channel of the primary link. If the backscatter symbols can be successfully decoded first, they can be modeled within the equivalent channel \eqref{eq:equivalent_channel} as in channel training, instead of being removed by SIC.
			\end{remark}

			To explicitly specify each backscatter symbol combination, we label it by the corresponding modulation index set. For tag $k$ at state $m_k$, $\forall k \in \mathcal{K}$, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k : k \in \mathcal{K}\}$ and the tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} : k \in \mathcal{K}\}$. Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$ with variance
			\begin{equation}
				\sigma_{m_{\mathcal{K}}}^2 \triangleq \Bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr) \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
				\label{eq:receive_variance}
			\end{equation}
			which denotes the expectation of the received power per primary block under tag modulation index set $\boldsymbol{m}$, and can be numerically evaluated based on the precoder, tag, channel, and noise knowledge. For the ease of exposition, we sort all possible $\sigma_{m_{\mathcal{K}}}^2$ in ascending order by a one-to-one mapping $\boldsymbol{m} \mapsto i$, denote the hypothesis that the tag input combination at status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them. This blind spot issue can be mitigated by multi-antenna techniques.} For the optimal Maximum-Likelihood (ML) detector, the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is \cite{Qian2019}
			\begin{equation}
				\Lambda_{i,j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_j^2}{\sigma_i^2 \sigma_j^2} z \right),
				\label{eq:likelihood_ratio}
			\end{equation}
			where $f(\boldsymbol{y} \mid \mathcal{H}_i)$ and $f(\boldsymbol{y} \mid \mathcal{H}_j)$ are respectively the conditional probability density function of receiving $\boldsymbol{y}$ under hypothesis $\mathcal{H}_i$ and $\mathcal{H}_j$, and $z \triangleq \lVert \boldsymbol{y} \rVert^2$ is the received signal energy over $N$ primary blocks. Obviously, the likelihood ratio only depends on $z$ and the energy detection is thus optimal. The corresponding decision rule is
			\begin{equation}
				\Lambda_{i,j}(z) \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,j},
				\label{eq:decision_rule}
			\end{equation}
			where the detection threshold between $\mathcal{H}_i$ and $\mathcal{H}_j$ is
			\begin{equation}
				T_{i,j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2}.
				\label{eq:detection_threshold}
			\end{equation}

			Accordingly, the decision region of hypothesis $\mathcal{H}_i$ is
			\begin{equation}
				\mathcal{R}_i \triangleq [T_{i-1, i}, T_{i, i+1}),
				\label{eq:decision_region}
			\end{equation}
			and we manually define $T_{0,1} \triangleq 0$ and $T_{M^K,M^K+1} \triangleq \infty$. Let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Since $z$ follows chi-squared distribution with $2N$ degrees of freedom, it holds that
			\begin{equation}
				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} \Gamma(N)},
				\label{eq:energy_distribution}
			\end{equation}
			where $\Gamma(\cdot)$ is the gamma function. As such, we can formulate an equivalent point-to-point discrete memoryless channel from tag input combination alphabet $\mathcal{M^K}$ to received energy level alphabet $\mathcal{M^K}$ as a transition matrix, where the probability of observing energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations. [TODO] Is this necessary? Maybe we can keep those same energy levels and avoid them by input distribution design.}
			\begin{equation}
				P(z_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
				\label{eq:equivalent_channel}
			\end{equation}

			Based on the equivalent point-to-point channel \eqref{eq:equivalent_channel}, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC. Mathematically speaking, the probability of observing energy level $j$ when tag $k$ at status $m_k$ is
			\begin{equation}
				P(z_j \mid c_k = \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus k}} P(z_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(z_j \mid \bar{c}_{m_{\mathcal{K}}})}.
				\label{eq:mac}
			\end{equation}

			In summary, for every possible tag input combination, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, the equivalent point-to-point channel can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:equivalent_channel}, and the discrete memoryless MAC can be extracted by \eqref{eq:mac}.
		\end{subsection}

		\begin{subsection}{Backscatter sum-capacity}
			Before investigating the sum-capacity of the tags, we introduce some definitions in information theory. Following \cite{Rezaeian2004}, the information function associated with individual tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
			\begin{equation}
				% I(\bar{c}_{m_{\mathcal{K}}} ; z) = \infdiv*{P(z \mid \bar{c}_{m_{\mathcal{K}}})}{P(z)}
				I(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(z_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(z_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(z_j)},
				\label{eq:information_function}
			\end{equation}
			and the marginal information function on $\mathcal{S} \subset \mathcal{K}$ is thus
			\begin{equation}
				I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{m_{\mathcal{K} \setminus \mathcal{S}}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I(\bar{c}_{m_{\mathcal{K}}} ; z).
			\end{equation}
			On top of this, the mutual information and marginal mutual information can be expressed respectively as
			\begin{align}
				I(c_{\mathcal{K}} ; z)
				& = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right],\\
				I(c_{\mathcal{S}} ; z)
				& = \mathbb{E}_{c_{\mathcal{S}}} \left[I(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
			\end{align}

@@

			Denote the input probability distribution of tag $k$ at status $m_k$ as $r_k(\bar{c}_{m_k})$.

			% For $\mathcal{S} \subset \mathcal{K}$, denote the input probability distribution that user $r_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}})$
		\end{subsection}
	\end{section}

>>>>

			Without loss of generality, we focus on the transmissions and detections during one particular backscatter symbol period. To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard CSCG distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-PSK modulation by \eqref{eq:mpsk}, i.e., $c_k \in \mathcal{C}$, $\forall k \in \mathcal{K}$. Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.}
			\begin{equation}
				y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k\right) \boldsymbol{w} s[n] + w[n],
				\label{eq:received_signal}
			\end{equation}
			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ is the equivalent Additive White Gaussian Noise (AWGN) at block $n$. Besides, we collect the backscatter symbols of $K$ tags into $c_{\mathcal{K}} \triangleq \{c_k : k \in \mathcal{K}\}$, stack the received signal over $N$ blocks as $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
			\begin{equation}
				\boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k.
				\label{eq:equivalent_primary_channel}
			\end{equation}

@@

			\begin{remark}
				One key property of symbiotic radio is the primary message propagates to the user from a known channel and multiple multiplicative channels with uncertainty introduced by backscatter modulation. As such, each reflection coefficient simultaneously encodes the tag message and influences the equivalent channel of the primary link. If the backscatter symbols can be successfully decoded first, they can be modeled within the equivalent channel \eqref{eq:equivalent_primary_channel} as in channel training, instead of being removed by SIC.
			\end{remark}

			To explicitly specify each backscatter symbol combination, we label it by the corresponding modulation index set. For tag $k$ at state $m_k$, $\forall k \in \mathcal{K}$, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k : k \in \mathcal{K}\}$ and the tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} : k \in \mathcal{K}\}$. Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$ with variance
			\begin{equation}
				\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
				\label{eq:receive_variance}
			\end{equation}
			which denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$, and can be numerically evaluated based on the precoder, tag, channel, and noise knowledge. For the ease of exposition, we sort all possible $\sigma_{m_{\mathcal{K}}}^2$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$, denote the hypothesis that the tag input combination at status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them. This blind spot issue can be mitigated by multi-antenna techniques.} For the optimal Maximum-Likelihood (ML) detector, the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is \cite{Qian2019}
			\begin{equation}
				\Lambda_{i,j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_j^2}{\sigma_i^2 \sigma_j^2} z \right),
				\label{eq:likelihood_ratio}
			\end{equation}
			where $f(\boldsymbol{y} \mid \mathcal{H}_i)$ and $f(\boldsymbol{y} \mid \mathcal{H}_j)$ are respectively the conditional probability density function of receiving $\boldsymbol{y}$ under hypothesis $\mathcal{H}_i$ and $\mathcal{H}_j$, and $z \triangleq \lVert \boldsymbol{y} \rVert^2$ is the received signal energy over $N$ primary blocks. Obviously, the likelihood ratio only depends on $z$ and the energy detection is thus optimal. The corresponding decision rule is
			\begin{equation}
				\Lambda_{i,j}(z) \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,j},
				\label{eq:decision_rule}
			\end{equation}
			where the detection threshold between $\mathcal{H}_i$ and $\mathcal{H}_j$ is
			\begin{equation}
				T_{i,j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2}.
				\label{eq:detection_threshold}
			\end{equation}

			Accordingly, the decision region of hypothesis $\mathcal{H}_i$ is
			\begin{equation}
				\mathcal{R}_i \triangleq [T_{i-1, i}, T_{i, i+1}),
				\label{eq:decision_region}
			\end{equation}
			and we manually define $T_{0,1} \triangleq 0$ and $T_{M^K,M^K+1} \triangleq \infty$. Let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Since $z$ follows chi-squared distribution with $2N$ degrees of freedom, it holds that
			\begin{equation}
				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} \Gamma(N)},
				\label{eq:energy_distribution}
			\end{equation}
			where $\Gamma(\cdot)$ is the gamma function. As such, we can formulate an equivalent point-to-point discrete memoryless channel from tag input combination alphabet $\mathcal{M^K}$ to received energy level alphabet $\mathcal{M^K}$ as a transition matrix, where the probability of observing energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations. [TODO] Is this necessary? Maybe we can keep those same energy levels and avoid them by input distribution design.}
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
				\label{eq:point_to_point_channel}
			\end{equation}

			Based on the equivalent point-to-point channel \eqref{eq:point_to_point_channel}, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC. Mathematically speaking, the probability of observing energy level $j$ when tag $k$ at status $m_k$ is
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus k}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}.
				\label{eq:mac}
			\end{equation}

			In summary, for every possible tag input combination, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, the equivalent point-to-point channel can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:point_to_point_channel}, and the discrete memoryless MAC can be extracted by \eqref{eq:mac}.
		\end{subsection}

		\begin{subsection}{Backscatter sum-capacity}
			Before investigating the sum-capacity of the tags, we introduce some prerequisites in information theory. Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, and assume the input distribution of all tags are mutually independent, such that $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Following \cite{Rezaeian2004}, the information function associated with specific tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
			\begin{equation}
				I(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)},
				\label{eq:information_function}
			\end{equation}
			the marginal information function on $\mathcal{S} \subset \mathcal{K}$ can be written as
			\begin{equation}
				I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I(\bar{c}_{m_{\mathcal{K}}} ; z),
				\label{eq:marginal_information_function}
			\end{equation}
			and the mutual information of the tags and the received signal can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ (and $\bar{c}_i$), $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
			\begin{equation}
				I(c_{\mathcal{K}} ; z) = \mathbb{E}_{c_{\mathcal{K}}} \left[I(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
			\end{equation}

			Evidently, for a given discrete memoryless MAC with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $P_k(\bar{c}_{m_k})$, $\forall m_k \in \mathcal{M}, k \in \mathcal{K}$. Therefore, we can obtain the backscatter sum-capacity by maximizing the mutual information over the tag input distributions as
			\begin{equation}
				R_c = \max_{P(c_{\mathcal{K}})} I(c_{\mathcal{K}} ; z) \ [\si{bpcu}].
			\end{equation}

			% On top of them, the mutual information and marginal mutual information can be written respectively as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ (and $\bar{c}_i$), $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
			% \begin{align}
			% 	I(c_{\mathcal{K}} ; z)
			% 	& = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right],\\
			% 	I(c_{\mathcal{S}} ; z)
			% 	& = \mathbb{E}_{c_{\mathcal{S}}} \left[I(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
			% \end{align}

			% On top of \eqref{eq:information_function} and \eqref{eq:marginal_information_function}, the mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ (and $\bar{c}_i$), $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
			% \begin{equation}
			% 	I(c_{\mathcal{K}} ; z) = \mathbb{E}_{c_{\mathcal{K}}} \left[I(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
			% \end{equation}

@@

			% For $\mathcal{S} \subset \mathcal{K}$, denote the input probability distribution that user $r_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}})$
		\end{subsection}

		\begin{subsection}{Primary ergodic capacity}
			Once the tag symbol set $\bar{c}_{m_{\mathcal{K}}}$ is successfully detected, the user can eliminate the backscatter uncertainty and obtain the equivalent primary channel by \eqref{eq:equivalent_primary_channel}. From the perspective of primary transmission, the tags adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block. As such, the ergodic primary capacity can be expressed as
			\begin{align}
				R_s
				& = \mathbb{E}_{c_{\mathcal{K}}} \left[\log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\right]\nonumber\\
				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right) \ [\si{bps/Hz}].
				\label{eq:primary_rate}
			\end{align}
			which is also a function of the tag input distribution $P_k(\bar{c}_{m_k})$, $\forall m_k \in \mathcal{M}, k \in \mathcal{K}$.
		\end{subsection}
		\label{se:system_model}
	\end{section}
